### 2014-03-16 Draft/abstract.tex
Revised abstract and part of intro

\begin{abstract}
Temporal specifications  or constraints of an Application Programming
Interface (API) describe allowed sequence of invocations
of methods within an API. These constraints govern the secure and robust
operation of client software using these APIs.
Despite being desirable for 
software testing and verification (through formal analysis tools),
most API's do not have formal temporal constraints.
In contrast, API documents contain valuable information (including temporal constraints) about the usage in natural language.
However, manually writing formal constraints based on natural language text in API documents
can be prohibitively time consuming and error prone.

On the other hand, automatically inferring temporal constraints from API documents is challenging.
In particular, it is challenging to automatically 
identify the methods referenced in the natural language text to infer temporal constraints.

@@

To address the preceding challenge, we propose a natural-language-processing-based approach \tool,
to infer formal temporal constraints from natural language text of API documents. These constraints can be used (as input)
by various software testing and verification tools to detect defects in client code the APIs.
Our approach 
addresses the preceding challenge by building (and leveraging) domain-dictionaries systematically from API
documents and generic English dictionaries.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
Our evaluation results are promising.
In particular, \tool\ achieves an average of 65\% precision and 72\% recall
in inferring 63 temporal constraints from more than 3900 sentences of API documents.

>>>>

\begin{abstract}
Temporal constraints of an Application Programming
Interface (API) are the allowed sequences of invocations
of methods from the API.
These constraints govern the secure and robust
operation of client software using the API.
Typically, these constraints are described in natural language text
of API documents and thus cannot be used by existing verification tools
which typically accept only formal constraints.
Because manually writing temporal constraints based on
API documents can be prohibitively time consuming and error prone,
we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer temporal constraints.
In particular, our approach includes novel techniques to reduce the number of lexical tokens
as a way to make API documents amenable to existing NLP techniques
(that are currently designed to work on well written news articles).
Our approach also includes a novel technique of identifying method references in
the natural language text by building domain-dictionaries systematically
from API documents and generic English dictionaries.
To evaluate our approach, we apply \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} in the JDK API and from the \amazonAPI.
Our results show that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 temporal constraints from these sentences.

@@

### 2014-03-16 Draft/conclusion.tex
Revised abstract and part of intro

Although highly desirable, most API's do not have formal specifications.
In contrast documentation of methods contain detailed specifications of the usage in natural language text.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we proposed a novel approach \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of 65\% precision and 72\% recall
in inferring 63 temporal constraints from more than 3900 sentences of API documents.

>>>>

Although highly desirable, most API's do not have formal temporal constraints.
In contrast, documentation of methods contain detailed specifications of the usage in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we proposed a novel approach \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} in the JDK API and from the Amazon S3 REST API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 65\% precision and 72\% recall,
from more than 3900 sentences in subject API documents.
Furthermore,\tool\ also achieved an  accuracy of
70\% in inferring 63 formal temporal constraints from these sentences.

### 2014-03-16 Draft/evaluation.tex
Revised abstract and part of intro

In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint).
The constraints that are enforced by the type-system can be enforced by IDEs.
Hence, for such types of constraints, we do not require sophisticated techniques like ICON. 
For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method $M$ accepting input parameter $I$ of type $T$ to be invoked after (at least one) a method $M'$ whose return value is of type $T$. 
Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint
if the constraint is implicit in the \CodeIn{CRUD} semantic followed by REST operations. 
\CodeIn{CRUD} stands for resource manipulation semantic sequence create, retrieve, update, and delete.
In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a GET operation on the same resource.

>>>>

In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint).
The constraints that are enforced by the type-system can be enforced by IDEs.
Hence, for such types of constraints, we do not require sophisticated techniques like ICON. 
For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method $M$ accepting input parameter $I$ of type $T$ to be invoked after (at least one) a method $M'$ whose return value is of type $T$. 
Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint
if the constraint is implicit in the \CodeIn{CRUD} semantic followed by REST operations. 
\CodeIn{CRUD} stands for resource manipulation semantic sequence create, retrieve, update, and delete.
In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a POST operation on the same resource.

### 2014-03-16 Draft/example.tex
Revised abstract and part of intro

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the constraints in \amazon.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed but one of the responses on the forum encouraged the person asking query to switch to another product,
thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.

The preceding issue can be easily detected using formal analysis tools.
For instance, a specification rule (temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
In next section, we briefly discuss the related work pertinent to our proposed approach.

>>>>

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazon, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
The issue was fixed.
However, one of the forum responses contained a recommendation for the inquisitor to switch to another product.
Customer dissatisfaction, such as was caused by this issue with the delete bucket functionality, can lead to a lose in revenue.

The preceding issue can be easily detected using formal analysis tools.
For instance, a specification rule (temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
%However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
%Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
In next section, we briefly discuss the related work pertinent to our proposed approach.

### 2014-03-16 Draft/introduction.tex
Revised abstract and part of intro

% Introduction needs to tightned up a bit
% Paragraph about typed languages must be moved to background or methodology
% Example might appropriately go in background as well
% Try to fit the goal statement in the introduction
% too long an abstract
% Names of exact tools and citations to them for verification
% Over use of however,
% J2EE document seems to be out of place

Temporal specifications or constraints~\cite{ball2002s} of an Application Programming Interface (API) 
describe allowed sequences of invocations of methods within an API. 
These constraints govern the secure and robust operation of client software 
using these APIs.
If these constraints are formal (machine-readable such as linear temporal logic),
they can be used  as a basis of formal analysis tools such 
as model checker and runtime verifiers
in detecting the violations of these temporal constraints as defects.

%Specifications of using an Application Programming Interface (API) of a library play an important role in software reuse.
%In addition to guiding the development process by outlining what and how to reuse, 
%usage specifications also help in verification process by allowing quality assurance practitioners to test the expected outcome.
%Furthermore, if the specifications are formal (machine-readable such as code-contracts),
%they can be used in conjunction with the formal analysis tools such as model checkers and runtime verifiers
%to automatically  reason about the quality of software.

%Formal specifications of an Application Programming Interface (API) usage are highly desirable.
%because they are the precursor to the formal analysis tools such as model checkers and runtime verifiers.

Despite being desirable, most API's do not have formal constraints.
In contrast, API developers commonly describe correct temporal usage in natural language text in API documents.
Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
%For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
For a method under consideration, an API document may describe both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the method.
We observed that a eminent portion (roughly 12\%) of the sentences (that describe some sort of constraints) in \amazonAPI\ documentations describe temporal constraints.
Although API documents contain temporal constraints, existing formal analysis tools accept only formal constraints but not informal constraints written in natural language.

One way of addressing the issue, is to manually convert the natural language API description into formal constraints. 
However, manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.

%Strike out ``To address the aforementioned issue''
%We propose a novel approach to infer temporal usage constraints from natural language text of API documents. 
To reduce the manual effort, we propose an automated approach that applies Natural Language Processing (NLP) techniques on natural language text in API documents to infer formal temporal constraints. 
%In particular, we focus on specific type of constraints namely temporal constraints.
A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.}
In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.

>>>>

Temporal constraints~\cite{ball2002s} of an Application Programming Interface (API) 
are the allowed sequences of invocations of methods within the API. 
These constraints govern the secure and robust operation of client software using the API.
If these constraints are formal (machine-readable such as linear temporal logic),
they can be used as inputs to the formal analysis tools such 
as model checker and runtime verifiers
in detecting the violations of these temporal constraints as defects~\cite{lee2012towards}.

Typically, these constraints are described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, an API document may describe both the constraints on that method parameters
as well as the temporal constraints in terms of methods that must be invoked pre/post that method.
We observed that an considerable portion (roughly 12\%) of the sentences (that describe some sort of constraints)
in \amazonAPI\ documentations describe temporal constraints.
However, existing verification tools which typically accept only formal constraints
cannot use the natural language constraints from API documents.

One way of addressing the issue, is to manually convert the natural language API description into formal constraints. 
However, manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.
To reduce the manual effort, we propose \tool: a Natural Language Processing (NLP) based approach
to automatically infer formal temporal constraints. 
%Strike out ``To address the aforementioned issue''
%We propose a novel approach to infer temporal usage constraints from natural language text of API documents.

%In particular, we focus on specific type of constraints namely temporal constraints.
%A generic temporal constraint is defined as \textit{an interpropositional constraint that communicates the ordering in time of events or states.}
%In terms of API method constraints, we interpret temporal constraints as \textit{`the allowed sequence of invocations of methods'}.
%For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
%We can interpret this sentence stating that a multipart-upload method must be invoked before invoking any part-upload method in the API.

### 2014-03-16 Draft/related.tex
Revised abstract and part of intro

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well-formed.
Additionally, these approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.

Most closely related work to the approach presented here is Pandita et al.~\cite{pandita12:inferring} work on inferring parameter constraints from method descriptions in the API documents.
Our proposed approach differs from the previous approach as follows.
Our proposed approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
Our proposed approach is a significant extension to the infrastructure used in the previous work in following areas.
First, the proposed approach introduces hybrid shallow parsing that relies both on POS tags as well as Stanford-typed dependencies to construct intermediate representation.
Second, the proposed approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
Finally, the proposed approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

\textbf{Augmented Documentation}:
Improving the documentation related to a software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

>>>>

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well-formed.
Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.

Most closely related work to the approach presented here is our previous work on inferring parameter constraints from method descriptions in the API documents~\cite{pandita12:inferring}.
Our proposed approach differs from the previous approach as follows.
Our proposed approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
Our proposed approach is a significant extension to the infrastructure used in the previous work in following areas.
First, the proposed approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation.
Second, the proposed approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
Finally, the proposed approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

\textbf{Augmented Documentation}:
Improving the documentation related to a software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the Eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
